Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond

### 2024-01-07 main.tex
:pencil: Update background

\begin{section}{Introduction}
	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
	This is made possible by the recent advances in \gls{ris}, a real-time programmable metasurface made of low-power reflecting elements.
	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than conventional relays.
	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication, backscatter, sensing, and power transfer literature \cite{Wu2019,Wu2020c,Yang2020,Zheng2021,Jia2020,Liang2022,Liu2022a,Hua2023,Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as investigated \cite{Liu2019d,Karasik2020,Basar2020,Ma2020a,Zhang2021d,Hua2022,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
	Although fruitful outcomes have been harvested by fancy optimization tools, one fundamental yet critical unanswered question is the \emph{channel shaping} capability of \gls{ris}: To what extent can \gls{ris} reshape the wireless channel?

>>>>

\begin{section}{Introduction}
	The quest for reliable, high-speed, and ubiquitous wireless connectivity has been long-standing since Marconi's illuminating radio in 1895.
	Great successes have been made at transmitter and receiver sides over the past century, and the society is unprecedentedly close to the Shannon limit \cite{Shannon1948}.
	Today we are witnessing a paradigm shift from \emph{connectivity} to \emph{intelligence}, where the wireless environment is no longer a chaotic medium but a conscious agent that serves on demand.
	This is made possible by the recent advances in \gls{ris}, a real-time programmable metasurface made of low-power reflecting elements.
	It can manipulate the amplitude, phase, frequency, and polarization of the scattered waves \cite{Basar2019} with a higher energy efficiency, lower cost, lighter footprint, and greater scalability than conventional relays.
	Using \gls{ris} for \emph{passive beamforming} has attracted significant interest in wireless communication, backscatter, sensing, and power transfer literature \cite{Wu2019,Wu2020c,Yang2020,Zheng2021,Jia2020,Liang2022,Liu2022a,Hua2023,Wu2021d,Feng2022,Zhao2022}, reporting a second-order array gain and fourth-order power scaling law (with proper waveform).
	On the other hand, \gls{ris} also enables \emph{backscatter modulation} by dynamically switching between different patterns, as already investigated \cite{Liu2019d,Karasik2020,Basar2020,Ma2020a,Zhang2021d,Hua2022,Zhao2022a} and prototyped \cite{Tang2019a,Dai2020a}.
	Although fruitful outcomes have been harvested by fancy optimization tools, one fundamental yet critical unanswered question is the \emph{channel shaping} capability of \gls{ris}: To what extent can \gls{ris} reshape the wireless channel?
